---
title: "Introduction to the Linear Regression Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the Linear Regression Model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearRegression)
```

Creating a linear regression model using the "Iris" dataset 

"linreg" takes 2 inputs, the first is the formula and the second is the dataset. 

As soon as you create an object from it, it automatically initializes by filling up multiple field through calculations and using the given formula and dataset. 

"l1" is an object of the class "linreg" which has these different fields.

```{r}
l1<-linreg(formula = Petal.Length~Species, data = iris)
```

There are also different methods available which are used to return the values of the different fields, we shall showcase each of them

print() will print out the coefficients and coefficient names

```{r}
l1$print()
```

plot() outputs 2 plots 1) Residuls vs Fitted Values and 2) Standardized Residuals  vs Fitted Values 
```{r}
l1$plot()
```

resid()  returns the vector of the residuals 

```{r}
l1$resid()
```

pred() returns the predicted values

```{r}
l1$pred()
```

coef()  returns the coefficients as a named vector
```{r}
l1$coef()
```

summary() presents the coefficients with their standard error, t-value and p-value as well as the estimate of ˆσ and the degrees
of freedom in the model.

```{r}
l1$summary()
```